### 2024-06-10 ms.qmd
Updates

## Results
```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
specie <- c("delicata", "guichenoti")
groups <- c("Red", "Blue")
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(i in 1:length(specie)){
  for(j in 1:length(groups)){
    for(k in 1:length(hormone)){
      for(l in 1:length(temperature)){
        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
      }
    }
  }
}
```

>>>>

## Results

**Preliminary table**
```{r, tbl-data}
source(here("R", "data_process.R"))
summary_table <- data_num %>%
  filter(choice == 1) %>% # Filter to keep only correct choices
  group_by(trt, test_type) %>% # Group by treatment and test
  summarise(count = n()) %>% # Count the number of correct choices
  pivot_wider(names_from = test_type, values_from = count, values_fill = list(count = 0)) %>% # Spread tests to columns
data.frame()
write.csv(summary_table, file= "./output/Checking/summary_table.csv")
data_num_bias <- data_num %>%
  mutate(
    actual_choice_lat = case_when(
      pos_high_lat == "Right" & choice == 1 ~ "Right",
      pos_high_lat == "Right" & choice == 0 ~ "Left",
      pos_high_lat == "Left" & choice == 1 ~ "Left",
      pos_high_lat == "Left" & choice == 0 ~ "Right",
      TRUE ~ NA_character_
    ),
    actual_choice_dist = case_when(
      pos_high_risk == "Close" & choice == 1 ~ "Close",
      pos_high_risk == "Close" & choice == 0 ~ "Far",
      pos_high_risk == "Far" & choice == 1 ~ "Far",
      pos_high_risk == "Far" & choice == 0 ~ "Close",
      TRUE ~ NA_character_
    )
  )
summary_biases <- data_num_bias %>%
  group_by(trt) %>% # Group by treatment and test
  summarise(
    right_choices = sum(actual_choice_lat == "Right", na.rm = TRUE),
    left_choices = sum(actual_choice_lat == "Left", na.rm = TRUE),
    close_choices = sum(actual_choice_dist == "Close", na.rm = TRUE),
    far_choices = sum(actual_choice_dist == "Far", na.rm = TRUE)
  ) %>% # Count the number of correct choices
data.frame()
write.csv(summary_biases, file= "./output/Checking/summary_biases.csv")
```

```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_asso.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
specie <- c("delicata", "guichenoti")
groups <- c("Red", "Blue")
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(i in 1:length(specie)){
  for(j in 1:length(groups)){
    for(k in 1:length(hormone)){
      for(l in 1:length(temperature)){
        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
      }
    }
  }
}
```
